Average solar wind and geomagnetic activity influence on the equatorial plasma mass density at geosynchronous orbit

### 2016-08-04 paper/paper.tex
Adding significance test for two peaks

We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.  In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval.  The peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.

To increase the number events, we have remove the constraint that the events must occur in the MLT range from 06-12 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.  The result is shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}.

>>>>

We have also considered the hourly averages from the events shown in the bottom panel of Figure~\ref{DailyAveragedDstEvents}, which shown in the top panel of Figure~\ref{HourlyAveragedDstEvents}.  In the time period of elevated mass density within 6 hours of the start of the event, there are only $\sim$4 samples per hourly interval.  The peak value of $\sim$70 amu/cm$^3$ is associated with a single observation.

To increase the number of events, we have removed the constraint that the events must occur in the MLT range from 06-12 and the constraint that $D_{st}$ remained below the threshold value for 12 hours or longer.  The result is shown in the bottom panel of Figure~\ref{HourlyAveragedDstEvents}. The two spikes (one updwards after onset, one downwards before onset) were tested for significant deviation from two baselines, one 24-12 hours before onset, one 16-48 hours after onset. The probability of the left spike coming from the same distribution as the left baseline is 1.06\%, and 8.2\% from the right baseline, whereas the probability of the right spike coming from the left baseline is 1.89\% and 0.17\% from the right baseline.
